Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
commit start of rewrite

\subsection{Neural network to GP prior} 
\label{sec:nn2gp}
%
A Gaussian process characterizes a distribution over functions in terms of the first two moments. The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$. We aim to find a kernel based on the neural network to build the Gaussian process posterior. If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network} 
We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
\begin{equation} \label{eq-laplace-approx-function-space}
 g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
  \mu(\vx) = \vzeros \quad \text{and} \quad
  \kappa(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{equation}
where the kernel is the Neural Tangent Kernel (NTK) \citep{jacot2018neural} with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where they perform a local linearization of the neural network  $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$. Their mean prior function differ from ours, \cref{eq-laplace-approx-function-space}, as theirs comes from setting  $  \mu(\vx) = f^{\textrm{lin}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, \ie the difference between the linear model approximation and the neural network function at $\vx$. %which does not seem useful as a prior mean function, 
On the other hand, we set $\mu(\vx) = \vzeros$, as common in GP literature and derived from a feature map conversion. \todo{derived what?}

>>>>

\subsection{Neural Network to GP Prior} 
\label{sec:nn2gp}
%
A Gaussian process characterizes a distribution over functions in terms of the first two moments. The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$. We aim to find a kernel based on the neural network to build the Gaussian process posterior. A common approach to find a $q(\vw)$ is to perform a Laplace-GGN approximation. The approximation can be seen as taking the map solution of \cref{eq-empirical-risk}

A linear function in terms of parameters can easily be converted from the weight space to the function space as follows

\begin{equation}
\hat{f}_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw
\end{equation}

$g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network} 
We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
\begin{equation} \label{eq-laplace-approx-function-space}
 g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
  \mu(\vx) = \vzeros \quad \text{and} \quad
  \kappa(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{equation}
where the kernel is the Neural Tangent Kernel (NTK) \citep{jacot2018neural} with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where they perform a local linearization of the neural network  $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$. Their mean prior function differ from ours, \cref{eq-laplace-approx-function-space}, as theirs comes from setting  $  \mu(\vx) = f^{\textrm{lin}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, \ie the difference between the linear model approximation and the neural network function at $\vx$. %which does not seem useful as a prior mean function, 
On the other hand, we set $\mu(\vx) = \vzeros$, as common in GP literature and derived from a feature map conversion. \todo{derived what?}
